The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-12-17 paper/mri_paper.tex
placeholder figures
more

The role of the boundary layers changes with Pm. As Pm decreases, the width of the boundary layer becomes increasingly narrow (Figure \ref{u_secondorder_by_Pm}). The relative importance of the $u_y$ second order perturbation to the first order perturbation increases as well (CHECK, PLOT).

\begin{figure*}[h!]
\centering
\includegraphics[trim=6cm 0cm 6cm 0cm, scale=0.4]{u_secondorder_by_Pm_2.eps}
\caption{(Placeholder) The evolution of the second-order velocity perturbations by Pm.}\label{allorders_velocity}
\label{u_secondorder_by_Pm}
\end{figure*}

It appears that the second-order velocity perturbations are instrumental in the saturation of the MRI. The likely mechanism is a reduction in the background shear.

>>>>

The role of the boundary layers changes with Pm. As Pm decreases, the width of the boundary layer becomes increasingly narrow (Figure \ref{u_secondorder_by_Pm}). The geometry of the velocity in the $x-z$ plane begins as a series of MRI ``cells" whose structure is radially narrow in the bulk of the flow. These central cells then stretch and grow, until at $Pm \sim 10^{-5}$ the bulk cells dominate the flow. The relative importance of the $u_y$ second order perturbation to the first order perturbation increases as well (CHECK, PLOT).

\begin{figure*}[h]
\centering
\includegraphics[trim=2cm 0cm 6cm 0cm, scale=0.4]{u_secondorder_by_Pm_2.eps}
\caption{(Placeholder) The evolution of the second-order velocity perturbations by Pm.}\label{allorders_velocity}
\label{u_secondorder_by_Pm}
\end{figure*}

%It appears that the second-order velocity perturbations are instrumental in the saturation of the MRI. The likely mechanism is a reduction in the background shear.

From the behavior of the second order velocity perturbations (Figure \ref{u_secondorder_by_Pm}) in the bulk of the flow (i.e. apart from the boundary layers), we gather that the MRI is saturating via a background shear reduction.

\begin{figure*}
\centering
\includegraphics[trim=6cm 4cm 6cm 3cm, scale=0.5]{stress_uy_cuts.pdf}
\caption{(Placeholder) The total stress (left) and vertical cuts of the azimuthal velocity perturbations (right). The $u_y$ perturbations shown are first order (purple), second order (orange), and total (black). The blue shaded area represents the region where the second order and total perturbations are opposing the background shear because they are negative, and the red shaded region indicates where the second order and total perturbations are opposing the background shear because they are positive.}\label{allorders_velocity}
\label{stress_uy_cuts}
\end{figure*}
